Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2018-01-16 Thesis/Thesis.rnw
A4 🤦‍♂️

\documentclass[10pt,a4paper]{article}

\usepackage{multicol,float}
\floatplacement{figure}{H}

@@

\includegraphics[height=2.5in]{EPH}
\hspace{40pt}
\includegraphics[height=2.5in]{Medicine}

@@

The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen. Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.

@@

\setcounter{figure}{4}
\begin{figure*}
\input{\figuresDir/coverageByRegionRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimen}
\end{figure*}

@@

\setcounter{figure}{7}
\begin{figure*}[!b]
\begin{center}
\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimenWithSliding}
\end{center}
\end{figure*}

@@

After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, overall we found that longer rounding intervals diminished the net benefit of spatial analysis.

@@

@@

Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-RSV counties, where they produced inferior results. (Figure \ref{fig:coverageByRegionRegimenWithSliding}.)

@@

>>>>

\documentclass[10pt,letter]{article}

\usepackage{multicol,float}
\floatplacement{figure}{H}
\raggedcolumns

@@

\includegraphics[height=160pt]{EPH}
\hspace{40pt}
\includegraphics[height=160pt]{Medicine}

@@

The cause of this is in temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen. (Figure \ref{fig:coverageByRegionAAPInsight}.) Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.

@@

\setcounter{figure}{4}
\begin{figure*}
\begin{center}
\input{\figuresDir/coverageByRegionRegimen.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimen}
\end{center}
\end{figure*}

@@

\columnbreak

@@

After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis. (Figure \ref{fig:coverageByRoundingRegimen}.)

@@

\columnbreak

@@

Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties. (Figure \ref{fig:coverageByRegionRegimenWithSliding}.)

@@

\setcounter{figure}{7}
\begin{figure*}
\begin{center}
\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
\label{fig:coverageByRegionRegimenWithSliding}
\end{center}
\end{figure*}
